A Comparative Study of Game-Theoretic and Reinforcement Learning Approaches for Jam-Resilient Wireless Networks in IoT

### 2025-06-09 paper/main.tex
progress

\author{
  \IEEEauthorblockN{Muhammad Umar Yaksambi}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: mumaryaksambi.cd23@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Anuj Devpura}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: anujdevpura.cd23@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Sadashiv Todakar}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: sadashivtodakar.cd23@rvce.edu.in
  }
}

>>>>

\author{
  \IEEEauthorblockN{Muhammad Umar Yaksambi}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\textregistered\\
    Bengaluru, India\\
    Email: mumaryaksambi.cd23@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Anuj Devpura}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\textregistered\\
    Bengaluru, India\\
    Email: anujdevpura.cd23@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Sadashiv Todakar}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\textregistered\\
    Bengaluru, India\\
    Email: sadashivtodakar.cd23@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Dr. Chethana R Murthy}
  \IEEEauthorblockA{
    Dept. of CSE \\
    RV College Of Engineering\textregistered\\
    Bengaluru, India\\
    Email: chethanamurthy@rvce.edu.in
  }
  \and
  \IEEEauthorblockN{Dr. Nagaraja G.S}
  \IEEEauthorblockA{
    Dept. of CSE \\
    RV College Of Engineering\textregistered\\
    Bengaluru, India\\
    Email: nagarajags@rvce.edu.in
  }
}
